### 2021-04-12 input/proposal.tex
about consistent partitioning

\begin{theorem}[\underline{B}est \underline{e}ventual \underline{f}orwarding $(BEF) \iff CP$]
  Assuming reliable communication links where a correct \process $q$
  eventually receives the message $m$ \underline{s}ent to it by a
  \process $p$ ($s_{pq}(m) \implies r_{q}(m)$); a monotonically
  growing system ($G^t \subseteq G^{t+1}$); \processes eventually
  reach consistent partitioning if and only if each \process
  eventually forwards its best known partition.
\end{theorem}

\begin{proof}
  \begin{asparadesc}
  \item [$BEF \implies CP$:] When a \process $s_1$ becomes a source,
    it belongs to its own partition, for there exists no better
    partition than its own: $\forall p \in V: |\Pi_{s_1 s_1}| <
    |\Pi_{s_1 p}|$. It forwards such message to its neighbors. Since
    communication links are reliable, neighboring \processes
    eventually receive such notification. Most importantly, whatever
    the order of received messages, every \process $p_1$ -- such that
    there exists no better partition $s_2$ than the received one --
    delivers and forwards it: $\forall s_2 \in S: |\Pi_{p s_1}| <
    |\Pi_{p s_2}|$. The message originating from $s_1$ transitively
    reaches all such \processes through shortest paths. Since there
    exists only one best value per \process that can never be
    retracted, \processes eventually reach consistent
    partitioning. % \TODO{Rework this with $s_{pq}$ and $r_{pq}$.}
  \item [$CP \implies BEF$:] \TODO{By contradiction, if there is a
    \process $p$ that does not forward, then another \process $q$ may
    never gets its best because it needs the weight $W_{pq}$.}
  \end{asparadesc}
\end{proof}

@@

Algorithm~\ref{algo:add} shows the instructions that implement such
consistent partitioning when
\begin{inparaenum}[(i)]
\item weights are scalar values,
\item \processes only add new partitions to the system,
\item and \processes never join nor crash nor leave the system.
\end{inparaenum}
Figure~\ref{fig:add} illustrates its behavior on a system comprising 4
\processes $a$, $b$, $c$, and $d$. \Process~$a$ and \Process~$d$ become
the sources of their partition. They \NAMEB a notification
\underline{a}dd message: $\alpha_a^0$ and $\alpha_d^0$. They
initialize their own state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, \Process~$b$
receives $\alpha_{d}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. In
Figure~\ref{fig:addD}, \Process~$b$ discards $\alpha_{a}^{2}$, for it
does not improve its partition distance. \Processes $c$ and $d$ will
never hear of Source~$a$. Ultimately, \processes discard last
transiting messages. The system reached consistent partitioning.

>>>>

\begin{theorem}[\underline{B}est \underline{e}ventual \underline{f}orwarding $(BEF) \implies CP$]
  Assuming reliable communication links where a correct \process $q$
  eventually receives the message $m$ \underline{s}ent to it by a
  \process $p$ ($s_{pq}(m) \implies r_{q}(m)$); a monotonically
  growing system ($G^t \subseteq G^{t+1}$); \processes eventually
  reach consistent partitioning if each \process eventually forwards
  its best known partition.
\end{theorem}

\begin{proof}
  % \begin{asparadesc}
  % \item [$BEF \implies CP$:]
  When a \process $s_1$ becomes a source, it belongs to its own
  partition, for there exists no better partition than its own:
  $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It delivers,
  hence forwards such $\alpha$ message to its -- current or future --
  neighbors. Since communication links are reliable, neighboring
  \processes eventually receive such notification $\forall \langle
  s_1, q \rangle \in E, s_1 \in S \iff \eventually
  r_q(\alpha_{s_1}^{w_{s_1 q}})$. Most importantly, whatever the order
  of received messages, every \process $q'$ in this neighborhood --
  such that there exists no better partition $s_2$ than the received
  one -- delivers and forwards it: $\forall s_2 \in S: |\Pi_{q' s_1}|
  < |\Pi_{q' s_2}| \implies \eventually d_{q'}(\alpha_{s_1}^{w_{s_1
      q'}})$. By transitivity, the message originating from $s_1$
  transitively reaches all such \processes through their shortest
  paths: $\forall q'' \in V, s_1, s_2 \in S: |\Pi_{q'' s_1}| <
  |\Pi_{q'' s_2}| \implies \eventually d_{q''}(\alpha_{s_1}^{|\Pi_{s_1
      q''}|})$.  Since there exists only one best sum of weights per
  \process that can never be retracted, \processes eventually reach
  consistent partitioning.
  %% /!\ not equivalence for there exists other implementations.
  %% \item [$CP \implies BEF$:] By contradiction, if a \process $q \in
  %%   \Pi_{sp} = [s, \ldots, q, q', \ldots, p]$ with $s, q, p \in P_s$
  %%   does not forward its received $\alpha_s^{|\Pi_{sq}|}$, then
  %%   following \processes from $q'$ to $p$ may mistake another
  %%   partition for their  because it needs the weight $W_{pq}$.
  %% \end{asparadesc}
\end{proof}

@@

Algorithm~\ref{algo:add} shows the instructions that implement such
consistent partitioning when
\begin{inparaenum}[(i)]
\item weights are scalar values,
\item \processes only add new partitions to the system,
\item and \processes never crash nor leave the system.
\end{inparaenum}
Figure~\ref{fig:add} illustrates its behavior on a system comprising 4
\processes $a$, $b$, $c$, and $d$. \Process~$a$ and \Process~$d$
become the sources of their partition. They \NAMEB a notification
\underline{a}dd message: $\alpha_a^0$ and $\alpha_d^0$. They
initialize their own state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, \Process~$b$
receives $\alpha_{d}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. In
Figure~\ref{fig:addD}, \Process~$b$ discards $\alpha_{a}^{2}$, for it
does not improve its partition distance. \Processes $c$ and $d$ will
never hear of Source~$a$. Ultimately, \processes discard last
transiting messages. Despite the obvious lack of traffic optimization,
the system reach consistent partitioning.
